Methods for Large Scale Learning to Rank

### 2014-11-20 report/Chapters/Background.tex
rechtvaardiging twee versies NDCG

No single evaluation metric that we are going to describe is indisputably better or worse than any of the other metrics. Different benchmarking settings have used different evaluation metrics. Metrics introduced in this section will be used in chapters \ref{chap:benchmark_results} and \ref{chap:cross_comparison} of this thesis to compare Learning to Rank methods in terms of ranking accuracy.
\subsection{Normalized Discounted Cumulative Gain}
Cumulative gain and its successors discounted cumulative gain and normalized discounted cumulative gain are arguably the most widely used measures for effectiveness of ranking methods. Cumulative Gain, without discounting factor and normalisation step, is defined as\\

>>>>

No single evaluation metric that we are going to describe is indisputably better or worse than any of the other metrics. Different benchmarking settings have used different evaluation metrics. Metrics introduced in this section will be used in chapters \ref{chap:benchmark_results} and \ref{chap:cross_comparison} of this thesis to compare Learning to Rank methods in terms of ranking accuracy.
\subsection{Normalized Discounted Cumulative Gain}
\label{sec:ndcg}
Cumulative gain and its successors discounted cumulative gain and normalized discounted cumulative gain are arguably the most widely used measures for effectiveness of ranking methods. Cumulative Gain, without discounting factor and normalisation step, is defined as\\

### 2014-11-20 report/Chapters/CrossBenchmarkComparison.tex
rechtvaardiging twee versies NDCG

\ac{NDCG}@3, \ac{NDCG}@5, \ac{NDCG}@10 and \ac{MAP} are chosen as metrics on which the meta-analysis will be performed. These metrics seem to be the most frequently used evaluation metrics in most of the used benchmark data sets. An exception is the Yahoo! Learning to Rank Challenge data sets on which mainly \ac{ERR} is used as main evaluation metric. The lack of use of the \ac{ERR}-metric in other benchmarks makes it unsuitable for a cross-benchmark comparison. By making the decision to include \ac{NDCG} at three cut-off points and only a single \ac{MAP} entry, we implicitly attain a higher weight for \ac{NDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting is arbitrary and therefore undesirable, but the number of algorithm evaluation results gained by this makes it a pragmatic approach.

@@

\begin{enumerate}
\item A different evaluation methodology was used in the study compared to what was used in other studies using the same benchmark \cite{Geng2011, Lin2012}.
\item The study focussed on a different Learning to Rank task (e.g. rank aggregation or transfer ranking) \cite{De2011, De2010, Derhami2013, De2012, Chen2010, Ah-Pine2008, Wang2009c, De2013, Miao2013, Hoi2008, De2012b, Duh2011b, Argentini2012, Qin2010c, Volkovs2013, Desarkar2011, Pan2013, Lin2011b, Volkovs2012, Dammak2011}.
\item The study used an altered version of a benchmark that contained additional features \cite{Bidoki2009, Ding2010}.
\item The study provides no exact data of the evaluation results (e.g. results are only in graphical form) \cite{Wang2008, Wang2010, Xu2010, Kuo2009, Li2008, Xia2008, Zhou2011, Wu2011, Zhu2009, Karimzadehgan2011, Swersky2012, Pan2011, Ni2008, Ciaramita2008, Stewart2012, Petterson2009, Agarwal2010, Chang2009, Qin2008c, Adams2011, Sculley2009, Huang2008, Alejo2010, Sun2011, He2010b, Benbouzid2012, Geng2012, Chen2012, Xu2012, Shivaswamy2011}.
\item The study reported evaluation results in a different metric than the metrics chosen for this meta-analysis \cite{Yu2009, Thuy2009, Pahikkala2009, Kersting2009, Mohan2011}.
\item The study reported a higher performance on baseline methods than official benchmark runs \cite{Dubey2009, Banerjee2009, Peng2010b, Song2014, Bian2010, Bian2010b, Carvalho2008, Acharyya2012, Peng2010b, Tran2012, Asadi2013c}. Such cases are not necessarily caused by malicious intent, but might be caused by a mix-up of the two existing versions of the \ac{NDCG} metric (J{\"a}rvelin and Kek{\"a}l{\"a}inen \cite{Jarvelin2002} and Burges et al. \cite{Burges2005}). 
\item The study did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008, Wang2012b, Buffoni2011}.
\end{enumerate}

>>>>

\ac{NDCG}@3, \ac{NDCG}@5, \ac{NDCG}@10 and \ac{MAP} are chosen as metrics on which the meta-analysis will be performed. These metrics seem to be the most frequently used evaluation metrics in most of the used benchmark data sets. An exception is the Yahoo! Learning to Rank Challenge data sets on which mainly \ac{ERR} is used as main evaluation metric. The lack of use of the \ac{ERR}-metric in other benchmarks makes it unsuitable for a cross-benchmark comparison. By making the decision to include \ac{NDCG} at three cut-off points and only a single \ac{MAP} entry, we implicitly attain a higher weight for \ac{NDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting is arbitrary and therefore undesirable, but the number of algorithm evaluation results gained by this makes it a pragmatic approach.\\

We described in section \ref{sec:ndcg} that there are two definitions of the \ac{NDCG}-metric that vary slightly: one defined by J{\"a}rvelin and Kek{\"a}l{\"a}inen \cite{Jarvelin2002} and the other defined by Burges et al. \cite{Burges2005}. The official benchmarks evaluation runs of the different benchmark sets differ in the \ac{NDCG}-definition that is used. For example, on the official LETOR evaluation runs the definition by J{\"a}rvelin and Kek{\"a}l{\"a}inen \cite{Jarvelin2002} is used, where the official evaluation runs on WCL2R use the definition by Burges et al. \cite{Burges2005}. For fair comparison, it is of importance to only take into account evaluation results that report \ac{NDCG} scores using the same \ac{NDCG}-definition as the official evaluation runs of the benchmark, therefore we filter out evaluation results that do not fulfil this property. Note that this approach results in the \ac{IWN} and \ac{NWN} calculations taking into account evaluation results in both definitions of \ac{NDCG} (although only one definition is used per data set). This is not a problem, since both definitions of \ac{NDCG} are highly correlated and vary only slightly.

@@

\begin{enumerate}
\item A different evaluation methodology was used in the study compared to what was used in other studies using the same benchmark \cite{Geng2011, Lin2012}.
\item The study focussed on a different Learning to Rank task (e.g. rank aggregation or transfer ranking) \cite{De2011, De2010, Derhami2013, De2012, Chen2010, Ah-Pine2008, Wang2009c, De2013, Miao2013, Hoi2008, De2012b, Duh2011b, Argentini2012, Qin2010c, Volkovs2013, Desarkar2011, Pan2013, Lin2011b, Volkovs2012, Dammak2011}.
\item The study used an altered version of a benchmark that contained additional features \cite{Bidoki2009, Ding2010}.
\item The study provides no exact data of the evaluation results (e.g. results are only in graphical form) \cite{Wang2008, Wang2010, Xu2010, Kuo2009, Li2008, Xia2008, Zhou2011, Wu2011, Zhu2009, Karimzadehgan2011, Swersky2012, Pan2011, Ni2008, Ciaramita2008, Stewart2012, Petterson2009, Agarwal2010, Chang2009, Qin2008c, Adams2011, Sculley2009, Huang2008, Alejo2010, Sun2011, He2010b, Benbouzid2012, Geng2012, Chen2012, Xu2012, Shivaswamy2011}.
\item The study reported evaluation results in a different metric than the metrics chosen for this meta-analysis \cite{Yu2009, Thuy2009, Pahikkala2009, Kersting2009, Mohan2011}.
\item The study reported a higher performance on baseline methods than the official benchmark results \cite{Dubey2009, Banerjee2009, Peng2010b, Song2014, Bian2010, Bian2010b, Carvalho2008, Acharyya2012, Peng2010b, Tran2012, Asadi2013c}. Such cases are not necessarily caused by malicious intent, but might be caused by a mix-up of the two existing versions of the \ac{NDCG} metric (J{\"a}rvelin and Kek{\"a}l{\"a}inen \cite{Jarvelin2002} and Burges et al. \cite{Burges2005}). 
\item The study did not report any results on the baseline methods to compare to the official benchmark results \cite{Chakrabarti2008, Wang2012b, Buffoni2011}.
\end{enumerate}
